Density dependence

### 2020-11-09 analysis/supplementary-materials/appendix_density_dependence.Rmd
reorganized files to make R CMD check happier

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  include = FALSE,
  echo = FALSE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300)
library(tidyverse)
library(here)
library(conflicted)
library(bbmle)
library(dlnm)
library(mgcv)
library(broom)
library(broom.mixed)
library(lme4)
library(car)

source(here("R", "crossbasis.R"))
source(here("R", "utils.R"))

>>>>

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  include = FALSE,
  echo = FALSE,
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "",
  dpi = 300)
library(tidyverse)
library(here)
library(conflicted)
library(bbmle)
library(dlnm)
library(mgcv)
library(broom)
library(broom.mixed)
library(lme4)
library(car)

library(HeliconiaDemography)
